\SW: Crowd-sourcing the Discovery of Gravitational Lenses

### 2014-09-03 doc/sw-system.tex
Compiled

Scaling of system. Factors of ten: 10^4 volunteers, 10^3 achieve high skill,
10^2 make significant contribution. Good project size is few 10^4 subjects, to
enable completion by a crowd of this size in short time.

>>>>

Scaling of system. Factors of ten: $10^4$ volunteers, $10^3$ achieve high
skill, $10^2$ make significant contribution. Good project size is few $10^4$
subjects, to enable completion by a crowd of this size in short time.
